```{r}
#| message: false
#| echo: false
library(tidyverse, quietly = TRUE)
library(bayesrules)
```

# Introducing your team (2 min)

Introduce yourself to the team and tell them what is your most unrealistic new-year resolution.

Write below the team name, team-member names and the most unrealistic resolution among you all.

```{r}

team_name <- "team01"

facilitator_name <- "KEEGAN JOSEPH"
summarizer_name <- "KEI BURROWS"
annotator_name <- "PAYTON MOSS"
timer_name <- "REESE SNIDER"
speaker_name <- "KYM ALLEN" # (Leave this blank if team has 4 members)

most_unrealistic_resolution <- "Gain 10 pounds"

sprintf("This is team %s!", team_name)
sprintf("The facilitator is %s", facilitator_name)
sprintf("The summarizer is %s", summarizer_name)
sprintf("The annotator is %s", annotator_name)
sprintf("The timer is %s", timer_name)
sprintf("The speaker is %s", speaker_name)
sprintf("Our most unrealistic new year resolution is %s", 
        most_unrealistic_resolution)

```

## Choosing your prior (5-10 min)

Your client asks that you take into account their prior information in your analysis.
So let's use this prior information to choose a prior distribution.
There is not a single "best" way of doing this, here we just want you to come up with something reasonable that you can explain to your client.

1.  **Briefly summarize all your prior information.**

Its a beta distribution, last year the HotRod tires raced faster than the tiny tires 2 out of 10 times. The tiny tires are faster on a straight track. This year, with a different track, we expect the HotRod tires to race faster up to 6 out of 10 times.

2.  **Where would you center your prior for the probability that the hot rod tires would be faster than the tiny tires? Explain your reasoning.**

We would center the prior around 0.4 because it is between last year's performance and this year's peak expectation.

3.  **What are some strengths and pitfalls of your prior information?**

A strength is that we understand part of why the HotRod tires were slower from experience, a pitfall is that we have no data about the HotRod tires on a different track.

4.  **Play around with values for** $alpha$ **and** $beta$ **below that give you a prior that looks reasonable enough to you. Briefly explain why it is reasonable (just the intuition)**.

```{r}

alpha <- 9
beta <- 15
plot_beta(alpha, beta)

```

We chose Beta(9,15) because it includes the range of (0.2,0.6) and is roughly centered around 0.4.


## Data collection (5-10 min)


Whenever playing set **Player ID = racing_stats** and **Group ID = YourTeam_YourRole**, e.g. **Group ID = danica1_facilitator**.

First, each team member will do one trial with the Classic car on the Eight track:

<https://www.stat2games.sites.grinnell.edu/games/raceradvanced22.html>

Then each team member will race the **HotRod car** on the **Eight** track, once with the HotRod tires and once with the Tiny tires:

-   Facilitator and Annotator race *first* with the HotRod tires

-   Summarizer, Timer and Speaker (if present) race *first* with the Tiny tires

IMPORTANT: **Remember to note your finishing times!!!**

Then complete the code below.

```{r}

# Assign value 1 if the finishing time with the HotRod tires was shorter than
# your finishing time with the Tiny tires, 0 otherwise

facilitator <- 0
annotator <- 0
summarizer <- 1
timer <- 1
speaker <- 0

# Uncomment the following line if your team has 4 people
#n_hotrod_faster <- facilitator + annotator + summarizer + timer

# Uncomment the following line if your team has 5 people
n_hotrod_faster <- facilitator + annotator + summarizer + timer + speaker

# Uncomment the following line
sprintf("The number of team members who finished the race faster with the Hotrod tire  was %s", n_hotrod_faster)

```

## Posterior summary (5 min)

Now you're ready to combine your prior information with your observations.

Complete the code below, then answer the questions.

```{r}

# Assign the number of team members (4 or 5) to n
n <- 5

# The number of successes y is the number of times the hotrod tires 
# led to a faster finish time. 
# Summarize your posterior
summarize_beta_binomial(alpha, beta, y = n_hotrod_faster, n)

# Plot your posterior
plot_beta_binomial(alpha, beta, y = n_hotrod_faster, n)


```

-   **What does your posterior suggests in terms of the probability of finishing the Eight track race faster with the HotRod tires than with the Tiny ones, on a HotRod car?**

Our posterior is more confident than our prior, and they both center around the same point roughly. This suggests the probability of finishing faster with HotRod tires is 0.38.

-   **What are some limitations of this study?**

We don't take into account the margin of difference between the finishing times for each race. We also have quite a small sample size.

